### 2016-01-24 03-design.tex
Ai, typo update_pi <-> update_phi in 03

The distributed design features two instances of pipeline parallelism. First,
at the process level, sampling of the minibatch by the master is decoupled
from \textit{update\_phi} by the workers, so the master computes the minibatch
for the next iteration while the workers compute \textit{update\_phi} for the
current iteration. Second, at the threads level within the workers, loading of
$\pi$ and \textit{update\_phi} are split up into chunks, and the calculation
in \textit{update\_pi} for the current chunk is done simultaneously with
loading $\pi$ for the next chunk. The rationale for implementing pipeline
parallelism in these places of the program, is that loading $\pi$ is the
dominant contribution within the dominant stage \textit{update\_phi}, as
will be shown in Section~\ref{eval-pipeline}.  Since loading $\pi$ is the
performance bottleneck of the distributed algorithm, performing other work
in parallel shortens the critical path.

>>>>

The distributed design features two instances of pipeline parallelism. First,
at the process level, sampling of the minibatch by the master is decoupled
from \textit{update\_phi} by the workers, so the master computes the minibatch
for the next iteration while the workers compute \textit{update\_phi} for the
current iteration. Second, at the threads level within the workers, loading of
$\pi$ and \textit{update\_phi} are split up into chunks, and the calculation
in \textit{update\_phi} for the current chunk is done simultaneously with
loading $\pi$ for the next chunk. The rationale for implementing pipeline
parallelism in these places of the program, is that loading $\pi$ is the
dominant contribution within the dominant stage \textit{update\_phi}, as
will be shown in Section~\ref{eval-pipeline}.  Since loading $\pi$ is the
performance bottleneck of the distributed algorithm, performing other work
in parallel shortens the critical path.
